Coherent optical association of a single molecule

### 2020-11-10 paper.tex
NFC: Fix latex warning about figure position specifier
Comments from Jeremy

\begin{abstract}
  Fully controlled single molecules provide a promising platform
  for a variety of quantum science applications.
  As a step towards this goal, we report on coherent association
  of a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing the photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
  with more than $60~\mathrm{\%}$ of the molecule created in the motional ground state.
  This technique does not rely on narrow excited-state lines or Feshbach resonances
  and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

$a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0$~\cite{Hood2019}.

@@

\begin{table}[h]
  \centering
  \begin{tabular}{c|c|c}
    & Experiment & Theory \\ \hline
    $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 78.9 ~\mathrm{MHz}$ \\
    $\Omega_a$ & $2\pi \times 12.1(3) ~\mathrm{MHz}$ & $2\pi \times 3.32 ~\mathrm{MHz}$ \\
    $\Omega_m/\Omega_a$ & $11.6(3)$ & $ 23.8$
  \end{tabular}
  \caption{Comparison between theory and experiment of the Rabi frequencies $\Omega_m$ and $\Omega_a$ at $3.75$ mW tweezer power. The experimentally measured ratio $\Omega_m/\Omega_a$ is smaller than the theory prediction.}
  \label{tab:rabi_freqs}
\end{table}

>>>>

\begin{abstract}
  Fully controlled single molecules provide a promising platform
  for a variety of quantum science applications.
  As a step towards this goal, we report on coherent association
  of a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing the photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
  and are created with higher than $60~\mathrm{\%}$ probability in the motional ground state.
  This technique does not rely on narrow excited-state lines or Feshbach resonances
  and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

$a(\uparrow_{\Na} \downarrow_{\Cs}) \approx -700a_0$~\cite{Hood2019}.

@@

\begin{table}[ht]
  \centering
  \begin{tabular}{c|c|c}
    & Experiment & Theory \\ \hline
    $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 78.9 ~\mathrm{MHz}$ \\
    $\Omega_a$ & $2\pi \times 12.1(3) ~\mathrm{MHz}$ & $2\pi \times 3.32 ~\mathrm{MHz}$ \\
    $\Omega_m/\Omega_a$ & $11.6(3)$ & $ 23.8$
  \end{tabular}
  \caption{Comparison between theory and experiment of the Rabi frequencies $\Omega_m$ and $\Omega_a$ at $3.75$ mW tweezer power. The experimentally measured ratio $\Omega_m/\Omega_a$ is smaller than the theory prediction.}
  \label{tab:rabi_freqs}
\end{table}
